The transition redshift as a probe of reionization

### 2019-08-09 paper/ms.tex
Add section on papers to cite

>>>>

\section{To cite}
Papers that need to be cited:

The Cross-Correlation of High-Redshift 21 cm and Galaxy Surveys
\url{https://arxiv.org/abs/astro-ph/0611274}

Probing Reionization with the 21 cm-Galaxy Cross Power Spectrum
\url{https://arxiv.org/abs/0806.1055}

The HI Bias during the Epoch of Reionization, discusses the positive/negative
correlation transition as a function of $k$
\url{https://arxiv.org/abs/1907.05098}
